\chapter{Conclusion}\label{chap:conclusion}

\section{Summary}

This project developed a fully automated pipeline for the numerical determination of Forming Limit Curves using Nakazima and Marciniak test simulations in Abaqus/Explicit. The pipeline covers the complete workflow — from model building and solver submission to strain extraction and FLC plotting — and runs end-to-end on the ETH Euler HPC cluster with a single command. The Hosford-Coulomb VUMAT subroutine was successfully integrated. Both test configurations are supported through a shared pipeline parameterised by a \texttt{TEST\_TYPE} flag, with test-specific punch geometry and die dimensions automatically selected from the configuration.

% TODO: Summarise quantitative findings once all simulations are complete.

\section{Outlook}

Directions for future work include:
\begin{itemize}
  \item Completion and analysis of the full Nakazima and Marciniak simulation campaigns across all specimen widths and thicknesses.
  \item Comparison of numerically determined FLCs between the two test configurations to quantify the effect of strain path linearity.
  \item Calibration and validation of the HC material constants against experimental tensile, shear, and notched test data.
  \item Sensitivity analysis of the FLC with respect to friction coefficient, punch velocity, and mesh size.
  \item Integration of the numerical strain field data with the FLC identification criteria of Task~II (Volk-Hora~\cite{VolkHora2011}, Merklein~\cite{Merklein2010}, Pham-Sigvant~\cite{Pham2023}, Min-Stoughton~\cite{Min2017}).
  \item Comparison of numerical FLCs with experimental results from the Nakazima/Marciniak test bench of Task~I.
\end{itemize}
